PS753

### 2022-03-26 _academics/ps753/ps753.Rmd
HW5 and knit
Add link

- My ongoing [glossary](../ps753-glossary/index.html) page; feel free to comment, or make additions or corrections via comments or github.
- Some [useful R tidbits](../ps753-useful-r-tidbits/index.html) from the course material and related sources.
- [Homework 3](../ps753-hw3/index.html) for the course: a network analysis of the Florentine Wedding data.
- [Homework 4](../ps753-hw4/index.html) for the course: a centrality analysis of the Florentine Wedding data.
- [Homework 5](../ps753-hw5/index.html) for the course: brokerage and betweenness analysis of the Florentine Wedding data.

>>>>

- My ongoing [glossary](../ps753-glossary/index.html) page; feel free to comment, or make additions or corrections via comments or github.
- Some [useful R tidbits](../ps753-useful-r-tidbits/index.html) from the course material and related sources.
- [Homework 3](../ps753-hw3/index.html) for the course: a network analysis of the Florentine Wedding data.
- [Homework 4](../ps753-hw4/index.html) for the course: a centrality analysis of the Florentine Wedding data.
- [Homework 5](../ps753-hw5/index.html) for the course: constraint and brokerage analysis of the Florentine Wedding data.
- [Homework 6](../ps753-hw6/index.html) for the course: clustering and blockmodel analysis of the Florentine Wedding data.
